---
title: "aa_analysis"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file takes the output from these five approach-avoid sim scripts - E1_aa_run.R; E2_aa_noisy_intent.R; E2_aa_noisy_stim; E3_imitate_run_animacy; E3_imitate_run_noisy_faces (or the aa_sim.Rmd file, which does the same thing), wrangles the data, produces various plots and runs some statistical analyses. 

Note - some of these plots and analyses are the identical or similar to what the base R plotting files already produce. This is just a different way of going about it. And it does a few extra things, such as saves more files etc.

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## section 1 ##

## take a look at simulated approach-avoid data from the basic model ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_aa_basic <- read_csv("sims/app_avoid/data/out_aa_basic.csv") 
head(out_aa_basic)
rts_aa_basic <- read_csv("sims/app_avoid/data/rts_aa_basic.csv")
head(rts_aa_basic)
roc_aa_basic <- read_csv("sims/app_avoid/data/roc_aa_basic.csv")
head(roc_aa_basic)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_aa_basic %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

Just FYI, this is different to the way the imitation activation timecourses 
were plotted. 
For now, I'll try to replicate what is in the latest paper.

plots p1.1 to p1.3 would mirror the way the imitation activation timecourse was 
plotted. We'll skip this for now, as we didn't produce it in the paper.

Instead, we'll skip straight to timecourse as a function of task (congr, incon)
and response (correct, incorrect)

```{r}
timecourse_task <- out_aa_basic %>% 
  select(task, cycle, correct_resp, incorrect_resp) %>% 
  group_by(task, cycle) %>%
  summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
  pivot_longer(cols = c("correct", "incorrect"),
               names_to = "response", values_to = "activation") %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         response = factor(response, levels = c("correct", "incorrect"))) %>% 
  select(task, response, cycle, activation) # just re-order slightly
head(timecourse_task)
```

plot the data

```{r}
p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
  geom_line() +
  ggtitle('Mean response activation by approach-avoid condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="bottom") +
  facet_wrap(~task)
p1.4

ggsave ("sims/app_avoid/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response)) +
  # ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"))  
p1.5

ggsave ("sims/app_avoid/figures/timecourse_task2.jpeg")
```


## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_aa_basic
head(roc)
```

plot RT against accuracy

```{r}
p2.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=42.95", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p2.1

ggsave ("sims/app_avoid/figures/roc_rt.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p2.2 <- ggplot(roc, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(title = "congruency effect vs. accuracy curve",
       x = "Congruency Effect (cycles)", y = "Accuracy (%)") +
  theme_bw()
p2.2

ggsave ("sims/app_avoid/figures/roc_ce.jpeg")
```

combined ROC plots

```{r}
p2.3 <- p2.1 | p2.2
p2.3

ggsave ("sims/app_avoid/figures/roc.jpeg")
```

## combine activation and ROC plots ##

This might be more efficient in a paper. 

```{r}
p2.4 <- p1.5 | p2.1 / p2.2
p2.4 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
# p2.4

ggsave ("sims/app_avoid/figures/timecourse_roc.jpeg")
```

## rt distrubition plots ##

density

```{r}
p3.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p3.1
```

boxplot

```{r}
# with acc=1
p3.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p3.2
```

violin plot

```{r}
# with acc=1
p3.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p3.3

ggsave ("sims/app_avoid/figures/rt_cycles.jpeg")

# split by acc (if necessary)
p3.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p3.3b

```

combined plots

rt distributions

```{r}
p3.4 <- p3.1 / p3.2 / p3.3
p3.4

ggsave ("sims/app_avoid/figures/rt_dist.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
p3.5 <- p1.5 | p3.3
p3.5 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p3.5

ggsave ("sims/app_avoid/figures/timecourse_rt_violin.jpeg")
```

with a boxplot

```{r}
p3.6 <- p1.5 | p3.2
p3.6 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p3.6

ggsave ("sims/app_avoid/figures/timecourse_rt_box.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='incon' & acc == 1)$cycle, 
       subset(rts, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/app_avoid/data/roc.csv")
write_csv(rts, "sims/app_avoid/data/rts.csv")
write_csv(rts_summary, "sims/app_avoid/data/rts_summary.csv")
write_csv(tidy_t_cycle, "sims/app_avoid/data/tidy_t_cycle.csv")
# write_csv(timecourse, "sims/app_avoid/data/timecourse.csv")
write_csv(timecourse_task, "sims/app_avoid/data/timecourse_task.csv")
```


## section 2 ##

## take a look at simulated approach-avoid data when the intention aspect of the model is damaged ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_aa_intent <- read_csv("sims/app_avoid/data/out_aa_intent.csv") 
head(out_aa_intent)
rts_aa_intent <- read_csv("sims/app_avoid/data/rts_aa_intent.csv")
head(rts_aa_intent)
roc_aa_intent <- read_csv("sims/app_avoid/data/roc_aa_intent.csv")
head(roc_aa_intent)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_aa_intent %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

Just FYI, this is different to the way the imitation activation timecourses 
were plotted. 
For now, I'll try to replicate what is in the latest paper.

plots p1.1 to p1.3 would mirror the way the imitation activation timecourse was 
plotted. We'll skip this for now, as we didn't produce it in the paper.

Instead, we'll skip straight to timecourse as a function of task (congr, incon)
and response (correct, incorrect)

```{r}
timecourse_task <- out_aa_intent %>% 
  select(task, cycle, correct_resp, incorrect_resp) %>% 
  group_by(task, cycle) %>%
  summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
  pivot_longer(cols = c("correct", "incorrect"),
               names_to = "response", values_to = "activation") %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         response = factor(response, levels = c("correct", "incorrect"))) %>% 
  select(task, response, cycle, activation) # just re-order slightly
head(timecourse_task)
```

plot the data

```{r}
p4.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
  geom_line() +
  ggtitle('Mean response activation by approach-avoid condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="bottom") +
  facet_wrap(~task)
p4.4

ggsave ("sims/app_avoid/figures/timecourse_task_intent.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p4.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response)) +
  # ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"))  
p4.5

ggsave ("sims/app_avoid/figures/timecourse_task2_intent.jpeg")
```


## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_aa_intent
head(roc)
```

plot RT against accuracy

```{r}
p5.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=36.21", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p5.1

ggsave ("sims/app_avoid/figures/roc_rt_intent.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p5.2 <- ggplot(roc, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(title = "congruency effect vs. accuracy curve",
       x = "Congruency Effect (cycles)", y = "Accuracy (%)") +
  theme_bw()
p5.2

ggsave ("sims/app_avoid/figures/roc_ce_intent.jpeg")
```

combined ROC plots

```{r}
p5.3 <- p5.1 | p5.2
p5.3

ggsave ("sims/app_avoid/figures/roc_intent.jpeg")
```

## combine activation and ROC plots ##

This might be more efficient in a paper. 

```{r}
p5.4 <- p4.5 | p5.1 / p5.2
p5.4 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
# p5.4

ggsave ("sims/app_avoid/figures/timecourse_roc_intent.jpeg")
```

## rt distrubition plots ##

density

```{r}
p6.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p6.1
```

boxplot

```{r}
# with acc=1
p6.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p6.2
```

violin plot

```{r}
# with acc=1
p6.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p6.3

ggsave ("sims/app_avoid/figures/rt_cycles_intent.jpeg")

# split by acc (if necessary)
p6.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p6.3b

```

combined plots

rt distributions

```{r}
p6.4 <- p6.1 / p6.2 / p6.3
p6.4

ggsave ("sims/app_avoid/figures/rt_dist_intent.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
p6.5 <- p4.5 | p6.3
p6.5 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p6.5

ggsave ("sims/app_avoid/figures/timecourse_rt_violin_intent.jpeg")
```

with a boxplot

```{r}
p6.6 <- p4.5 | p6.2
p6.6 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p6.6

ggsave ("sims/app_avoid/figures/timecourse_rt_box_intent.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='incon' & acc == 1)$cycle, 
       subset(rts, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/app_avoid/data/roc_intent.csv")
write_csv(rts, "sims/app_avoid/data/rts_intent.csv")
write_csv(rts_summary, "sims/app_avoid/data/rts_summary_intent.csv")
write_csv(tidy_t_cycle, "sims/app_avoid/data/tidy_t_cycle_intent.csv")
# write_csv(timecourse, "sims/app_avoid/data/timecourse_intent.csv")
write_csv(timecourse_task, "sims/app_avoid/data/timecourse_task_intent.csv")
```

## section 3 ##

## take a look at simulated approach-avoid data when the stimulus aspect of the model is damaged ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_aa_stim <- read_csv("sims/app_avoid/data/out_aa_stim.csv") 
head(out_aa_stim)
rts_aa_stim <- read_csv("sims/app_avoid/data/rts_aa_stim.csv")
head(rts_aa_stim)
roc_aa_stim <- read_csv("sims/app_avoid/data/roc_aa_stim.csv")
head(roc_aa_stim)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_aa_stim %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

Just FYI, this is different to the way the imitation activation timecourses 
were plotted. 
For now, I'll try to replicate what is in the latest paper.

plots p1.1 to p1.3 would mirror the way the imitation activation timecourse was 
plotted. We'll skip this for now, as we didn't produce it in the paper.

Instead, we'll skip straight to timecourse as a function of task (congr, incon)
and response (correct, incorrect)

```{r}
timecourse_task <- out_aa_stim %>% 
  select(task, cycle, correct_resp, incorrect_resp) %>% 
  group_by(task, cycle) %>%
  summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
  pivot_longer(cols = c("correct", "incorrect"),
               names_to = "response", values_to = "activation") %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         response = factor(response, levels = c("correct", "incorrect"))) %>% 
  select(task, response, cycle, activation) # just re-order slightly
head(timecourse_task)
```

plot the data

```{r}
p7.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
  geom_line() +
  ggtitle('Mean response activation by approach-avoid condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="bottom") +
  facet_wrap(~task)
p7.4

ggsave ("sims/app_avoid/figures/timecourse_task_stim.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p7.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response)) +
  # ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"))  
p7.5

ggsave ("sims/app_avoid/figures/timecourse_task2_stim.jpeg")
```


## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_aa_stim
head(roc)
```

plot RT against accuracy

```{r}
p8.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=33.32", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p8.1

ggsave ("sims/app_avoid/figures/roc_rt_stim.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p8.2 <- ggplot(roc, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(title = "congruency effect vs. accuracy curve",
       x = "Congruency Effect (cycles)", y = "Accuracy (%)") +
  theme_bw()
p8.2

ggsave ("sims/app_avoid/figures/roc_ce_stim.jpeg")
```

combined ROC plots

```{r}
p8.3 <- p8.1 | p8.2
p8.3

ggsave ("sims/app_avoid/figures/roc_stim.jpeg")
```

## combine activation and ROC plots ##

This might be more efficient in a paper. 

```{r}
p8.4 <- p7.5 | p8.1 / p8.2
p8.4 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
# p8.4

ggsave ("sims/app_avoid/figures/timecourse_roc_stim.jpeg")
```

## rt distrubition plots ##

density

```{r}
p9.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p9.1
```

boxplot

```{r}
# with acc=1
p9.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p9.2
```

violin plot

```{r}
# with acc=1
p9.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p9.3

ggsave ("sims/app_avoid/figures/rt_cycles_stim.jpeg")

# split by acc (if necessary)
p9.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p9.3b

```

combined plots

rt distributions

```{r}
p9.4 <- p9.1 / p9.2 / p9.3
p9.4

ggsave ("sims/app_avoid/figures/rt_dist_stim.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
p9.5 <- p7.5 | p9.3
p9.5 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p9.5

ggsave ("sims/app_avoid/figures/timecourse_rt_violin_stim.jpeg")
```

with a boxplot

```{r}
p9.6 <- p7.5 | p9.2
p9.6 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 16))
#p9.6

ggsave ("sims/app_avoid/figures/timecourse_rt_box_stim.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='incon' & acc == 1)$cycle, 
       subset(rts, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/app_avoid/data/roc_stim.csv")
write_csv(rts, "sims/app_avoid/data/rts_stim.csv")
write_csv(rts_summary, "sims/app_avoid/data/rts_summary_stim.csv")
write_csv(tidy_t_cycle, "sims/app_avoid/data/tidy_t_cycle_stim.csv")
# write_csv(timecourse, "sims/app_avoid/data/timecourse_stim.csv")
write_csv(timecourse_task, "sims/app_avoid/data/timecourse_task_stim.csv")
```

## section 4 ##

## plot aa data from different sims together ##

this is just for ease of comparison

# activation timecourse data #

load in the data and add a noise variable

```{r}
timecourse_task_basic <- read_csv("sims/app_avoid/data/timecourse_task.csv") %>% 
  mutate(noise = "baseline")
head(timecourse_task_basic)

timecourse_task_intent <- read_csv("sims/app_avoid/data/timecourse_task_intent.csv") %>% 
  mutate(noise = "intention")
head(timecourse_task_intent)

timecourse_task_stim <- read_csv("sims/app_avoid/data/timecourse_task_stim.csv") %>% 
  mutate(noise = "stimulus")
head(timecourse_task_stim)
```

join them together and create a factor 

```{r}
timecourse_task_all <- rbind(timecourse_task_basic, timecourse_task_intent, timecourse_task_stim) %>%
  select(task, response, noise, cycle, activation) %>% # select and re-order
  mutate(task = factor(task, levels = c("congr", "incon")),
         response = factor(response, levels = c("correct", "incorrect")),
         noise = factor(noise, levels = c("baseline", "stimulus", "intention")))
head(timecourse_task_all)
```

plot

```{r}
p10.1 <- ggplot(timecourse_task_all, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response)) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position=c(0.55, 0.60), legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"))+
  facet_wrap(~noise)
p10.1

ggsave ("sims/app_avoid/figures/timecourse_task_all.jpeg") 
```


# rt (cycles) #

load the data and add a noise variable

```{r}
rts <- read_csv("sims/app_avoid/data/rts.csv") %>% 
  mutate(noise = "baseline")
head(rts)

rts_intent <- read_csv("sims/app_avoid/data/rts_intent.csv") %>% 
  mutate(noise = "intention")
head(rts_intent)

rts_stim <- read_csv("sims/app_avoid/data/rts_stim.csv") %>% 
  mutate(noise = "stimulus")
head(rts_stim)
```

join them together and create a factor

```{r}
rts_all <- rbind(rts, rts_intent, rts_stim) %>%
  select(simno, task, noise, acc, cycle) %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         noise = factor(noise, levels = c("baseline", "stimulus", "intention"))) %>% 
  filter(acc==1)
head(rts_all)
# summary(rts_all)
```

create summary data

```{r}
rts_all_summary <- rts_all %>%
  group_by(task, noise) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
rts_all_summary
```

plot

```{r}
p10.2 <- ggplot(rts_all, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_all_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_all_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=rts_all_summary, aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(0, 150)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("RT (cycles)") +
  facet_wrap(~noise)
p10.2

ggsave ("sims/app_avoid/figures/rt_cycles_all.jpeg")
```

# combine plots for cycles and activation across normal and noise conditions #

```{r}
p10.5 <- (p10.1 + theme(legend.position = "right")) / 
        (p10.2 + theme(legend.position = "right"))
p10.5

ggsave ("sims/app_avoid/figures/time_cycle_all.jpeg")
```

add the ce diff to the same plot

```{r}
p10.6 <- (p10.1 + theme(legend.position = "right")) / 
        (p10.2 + theme(legend.position = "right")) /
        p10.3b
p10.6

ggsave ("sims/app_avoid/figures/time_rt_ce_all.jpeg")
```


## section 5 ##

wrangle and plot aa "imitation" rt data together

# rt (cycles) #

load the data and add a noise variable

```{r}
rts_aa_imitate <- read_csv("sims/app_avoid/data/rts_aa_imitate.csv") %>% 
  mutate(noise = "baseline")
head(rts_aa_imitate)

rts_aa_imitate_stim <- read_csv("sims/app_avoid/data/rts_aa_imitate_noisy_faces.csv") %>% 
  mutate(noise = "stimulus")
head(rts_aa_imitate_stim)
```

join them together and create a factor

```{r}
rts_all <- rbind(rts_aa_imitate, rts_aa_imitate_stim) %>%
  select(simno, task, noise, acc, cycle) %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         noise = factor(noise, levels = c("baseline", "stimulus", "intention"))) %>% 
  filter(acc==1)
head(rts_all)
```

create summary data

```{r}
rts_all_summary <- rts_all %>%
  group_by(task, noise) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
rts_all_summary
```

plot

```{r}
p11.2 <- ggplot(rts_all, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_all_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_all_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=rts_all_summary, aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0, 100)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("RT (cycles)") +
  facet_wrap(~noise)
p11.2

# ggsave ("sims/app_avoid/figures/rt_aa_imitate_cycles_all.jpeg")
```

now wrangle and plot the difference score or congruency effect

first wrangle the diff score or ce

```{r}
rts_diff <- rts_all %>% 
  pivot_wider(names_from = "task",
              values_from = "cycle") %>% 
  mutate(ce = incon - congr)
rts_diff
# summary(rts_diff)
```

create a summary

```{r}
rts_diff_summary <- rts_diff %>%
  group_by(noise) %>% 
  summarise(mean_ce=mean(ce, na.rm=TRUE), sd=sd(ce, na.rm=TRUE), n=n(), sem=sd/sqrt(n))
rts_diff_summary  
```

then plot 

(with noise on the x-axis)

```{r}
p11.3 <- ggplot(rts_diff, aes(x = noise, y = ce)) +
  geom_violin() +
  geom_jitter(width=0.1, alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_diff_summary, aes(y=mean_ce), size =3) +
  geom_errorbar(data=rts_diff_summary, aes(y = mean_ce, ymin=mean_ce-sem, ymax=mean_ce+sem), width=.2) +
  theme_bw() +
  # scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(-10, 80)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("Congruency Effect (cycles)") 
  # facet_wrap(~noise)
p11.3

ggsave ("sims/app_avoid/figures/ce_aa_imitate_cycles_all.jpeg")
```

with noise as a facet_wrap (to help with a combined plot)

```{r}
p11.3b <- ggplot(rts_diff, aes(x = "", y = ce)) +
  geom_violin() +
  geom_jitter(width=0.1, alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_diff_summary, aes(y=mean_ce), size =3) +
  geom_errorbar(data=rts_diff_summary, aes(y = mean_ce, ymin=mean_ce-sem, ymax=mean_ce+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(-10, 80)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"),
        axis.title.x=element_blank(), axis.ticks.x=element_blank()) +
  ylab("Congruency Effect (cycles)") +
  facet_wrap(~noise)
p11.3b

# ggsave ("sims/app_avoid/figures/ce_aa_imitate_cycles_all.jpeg")
```

now combine RT and CE plots together

```{r}
p11.4 <- p11.2 / p11.3b
p11.4

ggsave ("sims/app_avoid/figures/rt_ce_aa_imitate_cycles_all.jpeg")
```

## section 6 ##

plot aa rt data with aa rt imitation data - maybe this would be useful and
more efficient?

## first, just quickly, using patchwork ##

rt

```{r}
# p12.1 <- p10.2 / p11.2
# p12.1
```

ce

```{r}
# p12.2 <- p10.3b / p11.3b
# p12.2
```

## second, by wrangling and combining dataframes ##

# rt (cycles) #

load the data and add a noise variable

```{r}
rts_aa <- read_csv("sims/app_avoid/data/rts.csv") %>% 
  mutate(noise = "aa_baseline")
head(rts_aa)

rts_aa_intent <- read_csv("sims/app_avoid/data/rts_intent.csv") %>% 
  mutate(noise = "aa_intention")
head(rts_aa_intent)

rts_aa_stim <- read_csv("sims/app_avoid/data/rts_stim.csv") %>% 
  mutate(noise = "aa_stimulus")
head(rts_aa_stim)

rts_aa_imitate <- read_csv("sims/app_avoid/data/rts_aa_imitate.csv") %>% 
  mutate(noise = "imi_baseline")
head(rts_aa_imitate)

rts_aa_imitate_stim <- read_csv("sims/app_avoid/data/rts_aa_imitate_noisy_faces.csv") %>% 
  mutate(noise = "imi_stimulus")
head(rts_aa_imitate_stim)
```

join them together and create a factor

```{r}
rts_all <- rbind(rts_aa, rts_aa_intent, rts_aa_stim, rts_aa_imitate, rts_aa_imitate_stim) %>%
  select(simno, task, noise, acc, cycle) %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         noise = factor(noise, levels = c("aa_baseline", "aa_stimulus", "aa_intention", "imi_baseline", "imi_stimulus"))) %>% 
  filter(acc==1)
head(rts_all)
# summary(rts_all)
```

create summary data

```{r}
rts_all_summary <- rts_all %>%
  group_by(task, noise) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
rts_all_summary
```

plot

```{r}
p12.2 <- ggplot(rts_all, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_all_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_all_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=rts_all_summary, aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(0, 150)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("RT (cycles)") +
  facet_wrap(~noise, nrow = 1)
p12.2

ggsave ("sims/app_avoid/figures/aa_imi_rt_cycles_all.jpeg")
```

## print session info ##

```{r}
sessionInfo()
```
