---
title: "aa_sim"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file runs src simulations for the approach-avoid task. 

There are five different types of simulation that can be run.

In the section 1, there are three simulations that follow a similar format. These
are the primary approach-avoid simulations.

1. Basic (serves as default or baseline).

2. Damaged Intentions. This adds noise to the intention aspect of the model (noisy_intent).

3. Damaged Stimuli Encoding. This adds noise to the face processing aspects of the model i.e., processing the external visual stimulus (noisy_stim).

In the section 2, there are two further simulations, which act as a test of
task-specificity. We re-run the 'imitation' task using the normal settings and 
with the noise disruption to the face stim. This is to show that the effects 
of the noise disruption are task-specific (ie affecting the approach-avoid task
but not the imitation task).

4. Re-do the basic imitation task.

5. Run the imitation task with noise disruption to the face stim unit.

## section 1 ##

## simulations 1, 2 & 3 ##

## clear everything to start with a fresh environment ##

```{r}
rm(list = ls())
```

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## Source the global experiment parameters ##

This avoids inconsistencies between the runs of E1 (basic aa) and E2 (noise disruption)

```{r}
source('sims/app_avoid/aa_task.R')
set.seed(55)
```

If running sim 1 (basic), skip the next section and leave it commented out.

If running sim 2 or 3, uncomment one of the two chunks, as appropriate.

## add damage for noisy sims ##

this section is only required for the noisy_intent or noisy_stim sims. If running the basic sims, then skip this section.

damaged intentions

```{r}
# DAMAGE
# In this case disruption is specific to the processing of intentions
# G$noisy_units = c("approach", "avoid")
# G$unit_noise = .5
```

damaged stimuli encoding

```{r}
# DAMAGE
# In this case disruption is specific to the processing of faces
# fa = angry, fh = happy 
G$noisy_units = c("fh", "fa")
G$unit_noise = .5
```

## setup a function ##

include one of the two chunks below.

for the basic sim (sim 1)

```{r}
# run_aa_sims = function(network, label, ext_units) {
#   network = reset(network)
#   network = clear_external(network)
#   ext_units = G[[ext_units]]
#   network = set_external(network, units = ext_units, act = G[['ext_acts']])
#   out = sim_batch(network, nsims = G[['nsims']], ncycles = G[['ncycles']])
#   out = cbind(data.frame(task = label), out)
#   return(out)
# }
```

for both of the damage sims (sims 2 and 3), where noise is added.

```{r}
run_aa_noise_sims = function(network, label, ext_units) {
  network = reset(network)
  network = clear_external(network)
  ext_units = G[[ext_units]]
  network = set_external(network, units = ext_units, act = G[['ext_acts']])
  out = sim_batch_noisy(network, nsims = G[['nsims']], ncycles = G[['ncycles']],
                        noisy_units = G[['noisy_units']],
                        xtra_unit_noise = G[['unit_noise']])
  out = cbind(data.frame(task = label), out)
  return(out)
}
```

## read networks and run the simulation ##

include one of the two chunks below.

for the basic sim (sim 1)

```{r}
# plan(multicore)
# nn = read_net(G[['nnfile']])
# congr_out = run_aa_sims(nn, "congr", 'congr_task')
# incon_out = run_aa_sims(nn, "incon", 'incon_task')
# out = rbind(congr_out, incon_out)
# message('Finished.')
```

for both of the damage sims (sims 2 and 3), where noise is added.

```{r}
plan(multicore)
nn = read_net(G[['nnfile']], verbose = FALSE)
congr_out = run_aa_noise_sims(nn, "congr", 'congr_task')
incon_out = run_aa_noise_sims(nn, "incon", 'incon_task')
out = rbind(congr_out, incon_out)
message('Finished.')
```

## Explicitly identify the activations representing correct and incorrect responses ##

This is useful for the next step of RT and accuracy analysis 

```{r}
out$correct_resp = out$aa13
out$incorrect_resp = out$aa53
```

## save data with a unique filename ##

include one of the three chunks below.

for the basic sim (sim 1)

```{r}
# if(G[['nsims']] > 10) {
#   save_filename = sprintf("sims/app_avoid/data/rdata/aa_sim_%s-%s.RData", 
#                           Sys.Date(), format(Sys.time(),"%H%M"))
#   save(nn, out, file = save_filename)
#   message("Simulation output and network saved as file %s", save_filename)
# }
```

for damage to intentions (sim 2), where noise is added to intentions.

```{r}
# if(G[['nsims']] > 10) {
#   save_filename = sprintf("sims/app_avoid/data/rdata/aa_intent_noise(%02d)_%s-%s.RData", 
#                           100*G$unit_noise,
#                           Sys.Date(), format(Sys.time(),"%H%M"))
#   save(nn, out, file = save_filename)
#   message(sprintf("Simulation output and network saved as file %s", 
#                   save_filename))
# }
```

for damage to face processing (sim 3), where noise is added to stimuli processing.

```{r}
if(G[['nsims']] > 10) {
  save_filename = sprintf("sims/app_avoid/data/rdata/aa_stim_noise(%02d)_%s-%s.RData",
                          100*G$unit_noise,
                          Sys.Date(), format(Sys.time(),"%H%M"))
  save(nn, out, file = save_filename)
  message(sprintf("Simulation output and network saved as file %s",
                  save_filename))
}
```

## write out the files of interest as .csv files ##

```{r}
# write_csv(out, "sims/app_avoid/data/out_aa_basic.csv")

# write_csv(out, "sims/app_avoid/data/out_aa_intent.csv")

write_csv(out, "sims/app_avoid/data/out_aa_stim.csv")
```

## load previously saved data ##

This could be useful if you want to re-calculate RT data without re-running the
simulations again. Just load one at a time.

```{r}
# out <- read_csv("sims/app_avoid/data/out_aa_basic.csv")

# out <- read_csv("sims/app_avoid/data/out_aa_intent.csv")
# 
# out <- read_csv("sims/app_avoid/data/out_aa_stim.csv")
```

## a quick overview of results (currently stored in variable "out") ##

A note on setting epsilon in the aa_analysis.R script. For out_aa_basic and 
out_aa_intent, it would should work fine as it is set. But for out_aa_stim, it
needs lowering to .00005. Edit the R code directly when analysing RT for this
simulation.

```{r}
plan(multicore)
source("sims/app_avoid/aa_analysis.R")
```

## save out rt data ##

comment out, as appropriate.

basic

```{r}
# write_csv(rt_data[[1]], "sims/app_avoid/data/rts_aa_basic.csv")
# write_csv(rt_data[[2]], "sims/app_avoid/data/roc_aa_basic.csv")
```

noisy intent

```{r}
# write_csv(rt_data[[1]], "sims/app_avoid/data/rts_aa_intent.csv")
# write_csv(rt_data[[2]], "sims/app_avoid/data/roc_aa_intent.csv")
```

noisy stim

```{r}
write_csv(rt_data[[1]], "sims/app_avoid/data/rts_aa_stim.csv")
write_csv(rt_data[[2]], "sims/app_avoid/data/roc_aa_stim.csv")
```


## section 2 ##

In section 2,  we re-run the 'imitation' task using the normal settings and 
with the noise disruption to the face stim. This is to show that the effects 
of the noise disruption are task-specific (ie affecting aa but not imitation).

For simplicity, we run this from a sourced R script. The script clears 
everything before running, so it should be standalone. 

## simulations 4 & 5 ##

## run the simulation ##

choose one of the below chunks

A uniquely named .RData file is automatically saved in /data/rdata/

sim 4 - basic task with standard settings

```{r}
plan(multicore)
source('sims/app_avoid/E3_imitate_run_animacy.R')
```

sim 5 - imitation task with noise added to face processing

```{r}
plan(multicore)
source('sims/app_avoid/E3_imitate_run_noisy_faces.R')
```

## save out .csv files ##

choose one of the below chunks

```{r}
#sim4
write_csv(out, "sims/app_avoid/data/out_aa_imitate.csv")
```

```{r}
#sim5
write_csv(out, "sims/app_avoid/data/out_aa_imitate_noisy_faces.csv")
```

## load previously saved data ##

This could be useful if you want to re-calculate RT data without re-running the
simulations again. Just load one at a time.

```{r}
# out <- read_csv("sims/app_avoid/data/out_aa_imitate.csv")

# out <- read_csv("sims/app_avoid/data/out_aa_imitate_noisy_faces.csv")
```

## calculate RT data ##

```{r}
plan(multicore)
source('sims/RTs.R')
rt_data = RTs_generate(out, task1 = "congr", task2 = "incon",
                       accuracy_required = .98, epsilon = .005)[[1]]
```

## save the RT data ##

choose one of the below chunks

```{r}
#sim4
write_csv(rt_data, "sims/app_avoid/data/rts_aa_imitate.csv")
```

```{r}
#sim5
write_csv(rt_data, "sims/app_avoid/data/rts_aa_imitate_noisy_faces.csv")
```

## print session info ##

```{r}
sessionInfo()
```
