---
title: "analysis"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file takes the output from the 'E1_imi_run.R' script (or the sim.Rmd file, which does the same thing), wrangles the data, produces various plots and runs some statistical analyses. 

Note - some of these plots and analyses are the identical or similar to what the base R plotting files already produce. This is just a different way of going about it. And it does a few extra things, such as saves more files etc.

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## section 1 ##

## take a look at simulated imitation data from the basic model ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_imi_basic <- read_csv("sims/imitation/data/out_imi_basic.csv") 
head(out_imi_basic)
rts_imi_basic <- read_csv("sims/imitation/data/rts_imi_basic.csv")
head(rts_imi_basic)
roc_imi_basic <- read_csv("sims/imitation/data/roc_imi_basic.csv")
head(roc_imi_basic)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_imi_basic %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

```{r}
activation <- out_imi_basic %>% 
  select(cycle, "Tfeat_array" = fA33, "Tsalience" = s33, "Tidentity" = fA,
         "Dfeat_array" = fI32, "Dsalience" = s32, "Didentity" = fI) %>% 
  pivot_longer(-cycle,
               names_to = c("condition", "parameter"),
               names_sep = 1)  # separate columns based on the first letter
head(activation)
```

## make factors and rename ##

```{r}
activation <- activation %>%
  mutate(condition = factor(condition, levels = c("T", "D")),
         parameter = factor(parameter, levels = c("feat_array", "salience", "identity"))) %>% 
  mutate(condition = fct_recode(condition, target = "T", distractor = "D"))
head(activation)
```

## summarise ##

```{r}
timecourse <- activation %>% 
  group_by(cycle, condition, parameter) %>% 
  summarise(value = mean(value))
head(timecourse)
```

## timecourse plot ##

We are plotting the timecourse for the basic imitation task (E1), looking at the average for all trials. We include relevant columns to show an object-oriented selection e.g., target vs distractor.

set some common theme elements for line plots. 

```{r}
theme_set(
  theme_bw() +
    theme(text=element_text(size=22, face = "bold"), 
        title=element_text(size=22),
        legend.position=c(0.85,0.55), legend.text = element_text(size=16),
        legend.title = element_text(size = 16, face = "bold"))
)
```

plot

```{r}
p1.1 <- ggplot(timecourse, aes(x = cycle, y = value, color = parameter)) + 
  geom_line() +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  # theme_bw() +
  theme(legend.position="right") +
  ylab("activation") +
  facet_wrap(~condition)
p1.1

ggsave ("sims/imitation/figures/timecourse.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p1.2 <- ggplot(timecourse, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition)) +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  ylab("activation") 
p1.2

ggsave ("sims/imitation/figures/timecourse2.jpeg")
```

and now re-plotted with a shorter x-axis and no title with thicker lines

```{r}
# legend within the figure
p1.3 <- ggplot(timecourse, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition), linewidth = 1.5) +
  # ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  ylab("activation") +
  theme(legend.position=c(0.8,0.55)) +
  xlim(0, 100) +
  scale_y_continuous(limits = c(-0.2, 0.65), breaks = seq(-0.2, 0.6, 0.2))
p1.3

ggsave ("sims/imitation/figures/timecourse2b.jpeg",
        width = 12, height = 7)
```

## now plot timecourse as a function of task and accuracy ##

wrangle

```{r}
timecourse_task <- out_imi_basic %>% 
  select(task, cycle, correct_resp, incorrect_resp) %>% 
  group_by(task, cycle) %>%
  summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
  pivot_longer(cols = c("correct", "incorrect"),
               names_to = "response", values_to = "activation") %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         response = factor(response, levels = c("correct", "incorrect"))) %>% 
  select(task, response, cycle, activation) # just re-order slightly
head(timecourse_task)
```

plot

```{r}
p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
  geom_line() +
  ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position="bottom") +
  facet_wrap(~task)
p1.4

ggsave ("sims/imitation/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response)) +
  ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") 
p1.5

ggsave ("sims/imitation/figures/timecourse_task2.jpeg")
```

and now re-plotted with a shorter x-axis and no title

```{r}
# legend within the figure
p1.6 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
  geom_line(aes(linetype=response), linewidth = 1.5) +
  # ggtitle('Mean response activation by condition') +
  scale_color_brewer(palette = "Dark2") +
  xlim(0, 100) +
  scale_y_continuous(limits = c(-0.2, 0.65), breaks = seq(-0.2, 0.6, 0.2))
p1.6

ggsave ("sims/imitation/figures/timecourse_task2b.jpeg",
        width = 12, height = 7)
```

combine timecourse plots

```{r}
p1.7 <- p1.3 | p1.6
p1.7 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))

ggsave ("sims/imitation/figures/timecourse_object_task.jpeg",
        width = 13, height = 8)
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_imi_basic
head(roc)
```

plot RT against accuracy

```{r}
p2.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=51", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(x = "RT (cycles)", y = "Accuracy (%)") +
  xlim(0,100)
p2.1

ggsave ("sims/imitation/figures/roc_rt.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p2.2 <- ggplot(roc, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(x = "Congruency Effect (cycles)", y = "Accuracy (%)") 
p2.2

ggsave ("sims/imitation/figures/roc_ce.jpeg")
```

combined ROC plots

```{r}
p2.3 <- p2.1 | p2.2
p2.3 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))

ggsave ("sims/imitation/figures/roc.jpeg",
        width = 10, height = 5)
```

## combine activation and ROC plots ##

This might be more efficient in a paper. 

```{r}
p2.4 <- p1.3 | p2.1 / p2.2
p2.4 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))
# p2.4

ggsave ("sims/imitation/figures/timecourse_roc.jpeg", width = 15, height = 10)
```

and here we also add the timecourse by task plot

```{r}
p2.5 <- p1.3 / p1.6 | p2.1 / p2.2
p2.5 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30),
        legend.box = "horizontal")
# p2.5

ggsave ("sims/imitation/figures/timecourse_roc_b.jpeg", width = 15, height = 10)
```

now do it via previously combined plots

```{r}
p2.6 <- p1.7 / p2.3
p2.6 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))

ggsave ("sims/imitation/figures/timecourse_roc_b2.jpeg", width = 15, height = 10)
```

## rt distrubition plots ##

density

```{r}
p3.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p3.1
```

boxplot

```{r}
# with acc=1
p3.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p3.2
```

violin plot

```{r}
# with acc=1
p3.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p3.3

ggsave ("sims/imitation/figures/rt_cycles.jpeg")

# split by acc (if necessary)
p3.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p3.3b

```

combined plots

```{r}
p3.4 <- p3.1 / p3.2 / p3.3
p3.4

ggsave ("sims/imitation/figures/rt_dist.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='incon' & acc == 1)$cycle, 
       subset(rts, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/imitation/data/roc.csv")
write_csv(rts, "sims/imitation/data/rts.csv")
write_csv(rts_summary, "sims/imitation/data/rts_summary.csv")
write_csv(tidy_t_cycle, "sims/imitation/data/tidy_t_cycle.csv")
write_csv(timecourse, "sims/imitation/data/timecourse.csv")
```

## section 2 ##

## take a look at simulated imitation data when the animacy bias is set higher ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_imi_hi <- read_csv("sims/imitation/data/out_imi_hi.csv") 
head(out_imi_hi)
rts_imi_hi <- read_csv("sims/imitation/data/rts_imi_hi.csv")
head(rts_imi_hi)
roc_imi_hi <- read_csv("sims/imitation/data/roc_imi_hi.csv")
head(roc_imi_hi)
```

## wrangle rt data ##

```{r}
# make factors
rts_hi <- rts_imi_hi %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts_hi)
str(rts_hi)

# summarise accuracy data
acc_summary_hi <- rts_hi %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary_hi)
  
# summarise cycle data
rts_summary_hi <- rts_hi %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary_hi)

# grand mean rt - useful for speed-accuracy plot
rts_mean_hi <- rts_hi %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean_hi)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc_hi <- rts_hi %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc_hi)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

```{r}
activation_hi <- out_imi_hi %>% 
  select(cycle, "Tfeat_array" = fA33, "Tsalience" = s33, "Tidentity" = fA,
         "Dfeat_array" = fI32, "Dsalience" = s32, "Didentity" = fI) %>% 
  pivot_longer(-cycle,
               names_to = c("condition", "parameter"),
               names_sep = 1)  # separate columns based on the first letter
head(activation_hi)
```

## make factors and rename ##

```{r}
activation_hi <- activation_hi %>%
  mutate(condition = factor(condition, levels = c("T", "D")),
         parameter = factor(parameter, levels = c("feat_array", "salience", "identity"))) %>% 
  mutate(condition = fct_recode(condition, target = "T", distractor = "D"))
head(activation_hi)
```

## summarise ##

```{r}
timecourse_hi <- activation_hi %>% 
  group_by(cycle, condition, parameter) %>% 
  summarise(value = mean(value))
head(timecourse_hi)
```

## timecourse plot ##

We are plotting the timecourse for the basic imitation task (E1), looking at the average for all trials. We include relevant columns to show an object-oriented selection e.g., target vs distractor.

```{r}
p4.1 <- ggplot(timecourse_hi, aes(x = cycle, y = value, color = parameter)) + 
  geom_line() +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position="right") +
  ylab("activation") +
  facet_wrap(~condition)
p4.1

ggsave ("sims/imitation/figures/timecourse_hi.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p4.2 <- ggplot(timecourse_hi, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition)) +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position=c(0.8,0.5))
p4.2

ggsave ("sims/imitation/figures/timecourse2_hi.jpeg")
```

and now re-plotted with a shorter x-axis and with noi title and thicker lines

```{r}
# legend within the figure
p4.3 <- ggplot(timecourse_hi, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition), linewidth = 1.5) +
  # ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  xlim(0, 100)
p4.3

ggsave ("sims/imitation/figures/timecourse2b_hi.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc_hi <- roc_imi_hi
head(roc_hi)
```

plot RT against accuracy

```{r}
p5.1 <- ggplot(roc_hi, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean_hi$mean_rt, y=rts_acc_hi$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean_hi$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=72", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc_hi$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(x = "RT (cycles)", y = "Accuracy (%)") +
  # theme_bw() +
  xlim(0,125)
p5.1

ggsave ("sims/imitation/figures/roc_rt_hi.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p5.2 <- ggplot(roc_hi, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc_hi, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(x = "Congruency Effect (cycles)", y = "Accuracy (%)") 
p5.2

ggsave ("sims/imitation/figures/roc_ce_hi.jpeg")
```

combined ROC plots

```{r}
p5.3 <- p5.1 | p5.2
p5.3 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))

ggsave ("sims/imitation/figures/roc_hi.jpeg",
        width = 10, height = 5)
```


## rt distrubition plots ##

density

```{r}
p6.1 <- ggplot(rts_hi, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p6.1
```

boxplot

```{r}
# with acc=1
p6.2 <- ggplot(subset(rts_hi, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p6.2
```

violin plot

```{r}
# with acc=1
p6.3 <- ggplot(subset(rts_hi, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary_hi, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary_hi, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary_hi, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p6.3

ggsave ("sims/imitation/figures/rt_cycles_hi.jpeg")

# split by acc (if necessary)
p6.3b <- ggplot(rts_hi, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary_hi, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary_hi, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p6.3b

```

combined plots

```{r}
p6.4 <- p6.1 / p6.2 / p6.3
p6.4

ggsave ("sims/imitation/figures/rt_dist_hi.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle_hi <- t.test(subset(rts_hi, task=='incon' & acc == 1)$cycle, 
       subset(rts_hi, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle_hi

# tidy the output with broom
tidy_t_cycle_hi <- tidy(t_test_cycle_hi)
tidy_t_cycle_hi
```

## write out the files of interest ##

```{r}
write_csv(roc_hi, "sims/imitation/data/roc_hi.csv")
write_csv(rts_hi, "sims/imitation/data/rts_hi.csv")
write_csv(rts_summary_hi, "sims/imitation/data/rts_summary_hi.csv")
write_csv(tidy_t_cycle_hi, "sims/imitation/data/tidy_t_cycle_hi.csv")
write_csv(timecourse_hi, "sims/imitation/data/timecourse_hi.csv")
```


## section 3 ##

## take a look at simulated imitation data when the animacy bias is set lower ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_imi_lo <- read_csv("sims/imitation/data/out_imi_lo.csv") 
head(out_imi_lo)
rts_imi_lo <- read_csv("sims/imitation/data/rts_imi_lo.csv")
head(rts_imi_lo)
roc_imi_lo <- read_csv("sims/imitation/data/roc_imi_lo.csv")
head(roc_imi_lo)
```

## wrangle rt data ##

```{r}
# make factors
rts_lo <- rts_imi_lo %>%
  mutate(task = factor(task, levels = c("congr", "incon")))
head(rts_lo)
str(rts_lo)

# summarise accuracy data
acc_summary_lo <- rts_lo %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary_lo)
  
# summarise cycle data
rts_summary_lo <- rts_lo %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary_lo)

# grand mean rt - useful for speed-accuracy plot
rts_mean_lo <- rts_lo %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean_lo)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc_lo <- rts_lo %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc_lo)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

```{r}
activation_lo <- out_imi_lo %>% 
  select(cycle, "Tfeat_array" = fA33, "Tsalience" = s33, "Tidentity" = fA,
         "Dfeat_array" = fI32, "Dsalience" = s32, "Didentity" = fI) %>% 
  pivot_longer(-cycle,
               names_to = c("condition", "parameter"),
               names_sep = 1)  # separate columns based on the first letter
head(activation_lo)
```

## make factors and rename ##

```{r}
activation_lo <- activation_lo %>%
  mutate(condition = factor(condition, levels = c("T", "D")),
         parameter = factor(parameter, levels = c("feat_array", "salience", "identity"))) %>% 
  mutate(condition = fct_recode(condition, target = "T", distractor = "D"))
head(activation_lo)
```

## summarise ##

```{r}
timecourse_lo <- activation_lo %>% 
  group_by(cycle, condition, parameter) %>% 
  summarise(value = mean(value))
head(timecourse_lo)
```

## timecourse plot ##

We are plotting the timecourse for the basic imitation task (E1), looking at the average for all trials. We include relevant columns to show an object-oriented selection e.g., target vs distractor.

```{r}
p7.1 <- ggplot(timecourse_lo, aes(x = cycle, y = value, color = parameter)) + 
  geom_line() +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position="right") +
  ylab("activation") +
  facet_wrap(~condition)
p7.1

ggsave ("sims/imitation/figures/timecourse_lo.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
p7.2 <- ggplot(timecourse_lo, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition)) +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") 
p7.2

ggsave ("sims/imitation/figures/timecourse2_lo.jpeg")
```

and now re-plotted with a shorter x-axis

```{r}
# legend within the figure
p7.3 <- ggplot(timecourse_lo, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition), linewidth = 1.5) +
  # ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  xlim(0, 100)
p7.3

ggsave ("sims/imitation/figures/timecourse2b_lo.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc_lo <- roc_imi_lo
head(roc_lo)
```

plot RT against accuracy

```{r}
p8.1 <- ggplot(roc_lo, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean_lo$mean_rt, y=rts_acc_lo$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean_lo$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=42.1", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc_lo$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(x = "RT (cycles)", y = "Accuracy (%)") +
  # theme_bw() +
  xlim(0,125)
p8.1

ggsave ("sims/imitation/figures/roc_rt_lo.jpeg")
```

plot the compatibility effect (CE) against accuracy

```{r}
p8.2 <- ggplot(roc_lo, aes(x = taskdiff, y = acc)) +
  geom_point() + 
  geom_point(shape=1, size = 3) +
  geom_vline(aes(xintercept=subset(roc_lo, acc >= 0.98)$taskdiff[1]), colour="blue") +
  geom_hline(aes(yintercept=0.98), colour="red") +
  labs(x = "Congruency Effect (cycles)", y = "Accuracy (%)") 
  # theme_bw()
p8.2

ggsave ("sims/imitation/figures/roc_ce_lo.jpeg")
```

combined ROC plots

```{r}
p8.3 <- p8.1 | p8.2
p8.3 + plot_annotation(tag_levels = 'A') &
  theme(plot.tag = element_text(size = 30))

ggsave ("sims/imitation/figures/roc_lo.jpeg",
        width = 10, height = 5)
```


## rt distrubition plots ##

density

```{r}
p9.1 <- ggplot(rts_lo, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p9.1
```

boxplot

```{r}
# with acc=1
p9.2 <- ggplot(subset(rts_lo, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p9.2
```

violin plot

```{r}
# with acc=1
p9.3 <- ggplot(subset(rts_lo, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary_lo, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary_lo, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary_lo, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p9.3

ggsave ("sims/imitation/figures/rt_cycles_lo.jpeg")

# split by acc (if necessary)
p9.3b <- ggplot(rts_lo, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary_lo, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary_lo, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p9.3b

```

combined plots

```{r}
p9.4 <- p9.1 / p9.2 / p9.3
p9.4

ggsave ("sims/imitation/figures/rt_dist_lo.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle_lo <- t.test(subset(rts_lo, task=='incon' & acc == 1)$cycle, 
       subset(rts_lo, task == 'congr' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle_lo

# tidy the output with broom
tidy_t_cycle_lo <- tidy(t_test_cycle_lo)
tidy_t_cycle_lo
```

## write out the files of interest ##

```{r}
write_csv(roc_lo, "sims/imitation/data/roc_lo.csv")
write_csv(rts_lo, "sims/imitation/data/rts_lo.csv")
write_csv(rts_summary_lo, "sims/imitation/data/rts_summary_lo.csv")
write_csv(tidy_t_cycle_lo, "sims/imitation/data/tidy_t_cycle_lo.csv")
write_csv(timecourse_lo, "sims/imitation/data/timecourse_lo.csv")
```





## section 4 ##

## plot data from different sims together ##

this is just for ease of comparison

# activation timecourse data #

load in the data and add a bias variable

```{r}
timecourse <- read_csv("sims/imitation/data/timecourse.csv") %>% 
  mutate(bias = "baseline")
head(timecourse)

timecourse_hi <- read_csv("sims/imitation/data/timecourse_hi.csv") %>% 
  mutate(bias = "high")
head(timecourse_hi)

timecourse_lo <- read_csv("sims/imitation/data/timecourse_lo.csv") %>% 
  mutate(bias = "low")
head(timecourse_lo)
```

join them together and create a factor 

```{r}
timecourse_all <- rbind(timecourse, timecourse_hi, timecourse_lo) %>%
  select(cycle, condition, parameter, bias, value) %>% 
  mutate(condition = factor(condition, levels = c("target", "distractor")),
         parameter = factor(parameter, levels = c("feat_array", "salience", "identity")),
         bias = factor(bias, levels = c("baseline", "high", "low")))
head(timecourse_all)
```

plot

```{r}
p10.1 <- ggplot(timecourse_all, aes(x = cycle, y = value, colour = parameter)) + 
  geom_line(aes(linetype=condition), linewidth = 1.5) +
  scale_color_brewer(palette = "Dark2") +
  # theme_bw() +
  theme(legend.position=c(0.55, 0.60)) +
  ylab("activation") +
  facet_wrap(~bias)
p10.1

ggsave ("sims/imitation/figures/timecourse_all.jpeg",
        width = 12, height = 7) 
```


# rt (cycles) #

load the data and add a bias variable

```{r}
rts <- read_csv("sims/imitation/data/rts.csv") %>% 
  mutate(bias = "baseline")
head(rts)

rts_hi <- read_csv("sims/imitation/data/rts_hi.csv") %>% 
  mutate(bias = "high")
head(rts_hi)

rts_lo <- read_csv("sims/imitation/data/rts_lo.csv") %>% 
  mutate(bias = "low")
head(rts_lo)
```

join them together and create a factor

```{r}
rts_all <- rbind(rts, rts_hi, rts_lo) %>%
  select(simno, task, bias, acc, cycle) %>% 
  mutate(task = factor(task, levels = c("congr", "incon")),
         bias = factor(bias, levels = c("baseline", "high", "low"))) %>% 
  filter(acc==1)
head(rts_all)
```

create summary data

```{r}
rts_all_summary <- rts_all %>%
  group_by(task, bias) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
rts_all_summary
```

change the theme settings for plotting

```{r}
theme_set(
  theme_bw() +
    theme(text=element_text(size=18, face = "bold"),
        legend.position="none")
)
```

plot

```{r}
p10.2 <- ggplot(rts_all, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_all_summary, aes(y=mean_rt), size =2) +
  geom_errorbar(data=rts_all_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=rts_all_summary, aes(y=mean_rt, group=1)) +
  scale_fill_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0, 150)) +
  ylab("RT (cycles)") +
  facet_wrap(~bias)
p10.2

ggsave ("sims/imitation/figures/rt_cycles_all.jpeg",
         width = 5, height = 3)
```

# combine plots for cycles and activation across normal and bias conditions #

```{r}
p10.5 <- (p10.1 + theme(legend.position = "right")) / 
        (p10.2 + theme(legend.position = "right"))
p10.5

ggsave ("sims/imitation/figures/time_cycle_all.jpeg")
```


## print session info ##

```{r}
sessionInfo()
```