---
title: "analysis"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file takes the output from the 'E1_imi_run.R' script (or the sim.Rmd file, which does the same thing), wrangles the data, produces various plots and runs some statistical analyses. 

Note - some of these plots and analyses are the identical or similar to what the base R plotting files already produce. This is just a different way of going about it. And it does a few extra things, such as saves more files etc.

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## Read in the data files ##

read in only data file or all 3 data files depending on how much wrangling needs doing. 

```{r}
out_imi_basic <- read_csv("sims/imitation/data/out_imi_basic.csv") 
head(out_imi_basic)
# rts <- read_csv("data/rts.csv")
# timecourse <- read_csv("data/timecourse.csv")
```

## select relevant variables to plot ##

```{r}
out_plot <- out_imi_basic %>% 
  select(cycle, "Tfeat_array" = fA33, "Tsalience" = s33, "Tidentity" = fA,
         "Dfeat_array" = fI, "Dsalience" = s32, "Didentity" = fI) %>% 
  pivot_longer(-cycle,
               names_to = c("condition", "parameter"),
               names_sep = 1)  # separate columns based on the first letter
head(out_plot)
```

## make factors and rename ##

```{r}
out_plot <- out_plot %>%
  mutate(condition = factor(condition, levels = c("T", "D")),
         parameter = factor(parameter, levels = c("feat_array", "salience", "identity"))) %>% 
  mutate(condition = fct_recode(condition, target = "T", distractor = "D"))
head(out_plot)
```

## summarise ##

```{r}
timecourse <- out_plot %>% 
  group_by(cycle, condition, parameter) %>% 
  summarise(value = mean(value))
head(timecourse)
```

## timecourse plot ##

We are plotting the timecourse for the basic imitation task (E1), looking at the average for all trials. We include relevant columns to show an object-oriented selection e.g., target vs distractor.

```{r}
p1 <- ggplot(timecourse, aes(x = cycle, y = value, color = parameter)) + 
  geom_line() +
  ggtitle('Mean response activation') +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="right") +
  ylab("activation") +
  facet_wrap(~condition)
p1

ggsave ("sims/imitation/figures/timecourse.jpeg")
```


