---
title: "sim"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file runs src simulations for the imitation task.

# clear everything to start with a fresh environment #

```{r}
rm(list = ls())
```

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## set the animacy bias ##

comment out as appropriate, depending on the type of imitation simulation that 
you want to run.

```{r}
# animacy_bias = .1 # basic / standard parameters used
# animacy_bias = .2 # Relative salience of the distractor is INCREASED
animacy_bias = .05 # Relative salience of the distractor is DECREASED
```

## save out a .RData file ##

```{r}
# save_filename = sprintf("sims/imitation/data/rdata/out_imi_basic_%s-%s.RData",
#                        Sys.Date(), format(Sys.time(),"%H%M"))

save_filename = sprintf("sims/imitation/data/rdata/out_animacy(%02d)_%s-%s.RData", 
                       100*animacy_bias, Sys.Date(), format(Sys.time(),"%H%M"))
```

## run the simulation ##

To ensure consistency between E2 comparisons, the experiment is sourced.
This is run at the top level rather than as a function so that the resulting
network and simulation results are accessible in the global environment for
ease of investigation.

```{r}
plan(multicore)
source("sims/imitation/imitation_task.R")
```

## write out the files of interest as .csv files ##

This is just so plots can be made in a tidyverse style.

comment out, as appropriate.

```{r}
# write_csv(out, "sims/imitation/data/out_imi_basic.csv")

# write_csv(out, "sims/imitation/data/out_imi_hi.csv")

write_csv(out, "sims/imitation/data/out_imi_lo.csv")
```

## a quick overview of the results ##

```{r}
plan(multicore)
source("sims/imitation/imitation_analysis.R")
```

## save out rt data ##

comment out, as appropriate

basic

```{r}
# write_csv(rt_data[[1]], "sims/imitation/data/rts_imi_basic.csv")
# write_csv(rt_data[[2]], "sims/imitation/data/roc_imi_basic.csv")
```

hi

```{r}
# write_csv(rt_data[[1]], "sims/imitation/data/rts_imi_hi.csv")
# write_csv(rt_data[[2]], "sims/imitation/data/roc_imi_hi.csv")
```

lo

```{r}
write_csv(rt_data[[1]], "sims/imitation/data/rts_imi_lo.csv")
write_csv(rt_data[[2]], "sims/imitation/data/roc_imi_lo.csv")
```

## print session info ##

```{r}
sessionInfo()
```