---
title: "sim"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file runs src simulations for the imitation task.

# clear everything to start with a fresh environment #

```{r}
rm(list = ls())
```

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## set the animacy bias ##

```{r}
animacy_bias = .1
```

## save out a .RData file ##

```{r}
save_filename = sprintf("sims/imitation/out_imi_basic_%s-%s.RData", 
                       Sys.Date(), format(Sys.time(),"%H%M"))
```

## run the simulation ##

To ensure consistency between E2 comparisons, the experiment is sourced.
This is run at the top level rather than as a function so that the resulting
network and simulation results are accessible in the global environment for
ease of investigation.

```{r}
source("sims/imitation/imitation_task.R")
```

## write out the files of interest as .csv files ##

This is just so plots can be made in a tidyverse style

```{r}
write_csv(out, "data/out_imi_basic.csv")
```

## a quick overview of the results ##

```{r}
source("sims/imitation/imitation_analysis.R")
```

## save out rt data ##

```{r}
write_csv(rt_data, "data/rtdata_imi_basic.csv")
```