---
title: "search_analysis"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file takes the output from these three search sim scripts - search_run.R; search_run_easy.R; search_run_hard.R - (or the search_sim.Rmd file, which does the same thing), wrangles the data, produces various plots and runs some statistical analyses. 

Note - some of these plots and analyses are the identical or similar to what the base R plotting files already produce. This is just a different way of going about it. And it does a few extra things, such as saves more files etc.

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## section 1 ##

## take a look at simulated search data from the basic model ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_search_basic <- read_csv("sims/search/data/out_search.csv") 
head(out_search_basic)
rts_search_basic <- read_csv("sims/search/data/rts_search.csv")
head(rts_search_basic)
roc_search_basic <- read_csv("sims/search/data/roc_search.csv")
head(roc_search_basic)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_search_basic %>%
  mutate(task = factor(task, levels = c("3", "10")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

This would need editing to be appropriate, given that it uses a different design
to the prior sims.

```{r}
# timecourse_task <- out_search_basic %>% 
#   select(task, cycle, correct_resp, incorrect_resp) %>% 
#   group_by(task, cycle) %>%
#   summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
#   pivot_longer(cols = c("correct", "incorrect"),
#                names_to = "response", values_to = "activation") %>% 
#   mutate(task = factor(task, levels = c("congr", "incon")),
#          response = factor(response, levels = c("correct", "incorrect"))) %>% 
#   select(task, response, cycle, activation) # just re-order slightly
# head(timecourse_task)
```

plot the data

```{r}
# p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
#   geom_line() +
#   ggtitle('Mean response activation by approach-avoid condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position="bottom") +
#   facet_wrap(~task)
# p1.4
# 
# ggsave ("sims/app_avoid/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
# p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
#   geom_line(aes(linetype=response)) +
#   # ggtitle('Mean response activation by condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
#         legend.title = element_text(size = 10, face = "bold"))  
# p1.5
# 
# ggsave ("sims/app_avoid/figures/timecourse_task2.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_search_basic
head(roc)
```

plot RT against accuracy

```{r}
p2.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=26.1", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p2.1

ggsave ("sims/search/figures/roc_rt.jpeg")
```

## rt distrubition plots ##

density

```{r}
p3.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p3.1
```

boxplot

```{r}
# with acc=1
p3.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p3.2
```

violin plot

```{r}
# with acc=1
p3.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p3.3

ggsave ("sims/search/figures/rt_cycles.jpeg")

# split by acc (if necessary)
p3.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p3.3b

```

combined plots

rt distributions

```{r}
p3.4 <- p3.1 / p3.2 / p3.3
p3.4

ggsave ("sims/search/figures/rt_dist.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
# p3.5 <- p1.5 | p3.3
# p3.5 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.5
# 
# ggsave ("sims/search/figures/timecourse_rt_violin.jpeg")
```

with a boxplot

```{r}
# p3.6 <- p1.5 | p3.2
# p3.6 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.6
# 
# ggsave ("sims/app_avoid/figures/timecourse_rt_box.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='10' & acc == 1)$cycle, 
       subset(rts, task == '3' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/search/data/roc.csv")
write_csv(rts, "sims/search/data/rts.csv")
write_csv(rts_summary, "sims/search/data/rts_summary.csv")
write_csv(tidy_t_cycle, "sims/search/data/tidy_t_cycle.csv")
# write_csv(timecourse, "sims/search/data/timecourse.csv")
# write_csv(timecourse_task, "sims/search/data/timecourse_task.csv")
```


## section 2 ##

## take a look at simulated search data from the easy model ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_search_easy <- read_csv("sims/search/data/out_search_easy.csv") 
head(out_search_easy)
rts_search_easy <- read_csv("sims/search/data/rts_search_easy.csv")
head(rts_search_easy)
roc_search_easy <- read_csv("sims/search/data/roc_search_easy.csv")
head(roc_search_easy)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_search_easy %>%
  mutate(task = factor(task, levels = c("3", "10")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

This would need editing to be appropriate, given that it uses a different design
to the prior sims.

```{r}
# timecourse_task <- out_search_basic %>% 
#   select(task, cycle, correct_resp, incorrect_resp) %>% 
#   group_by(task, cycle) %>%
#   summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
#   pivot_longer(cols = c("correct", "incorrect"),
#                names_to = "response", values_to = "activation") %>% 
#   mutate(task = factor(task, levels = c("congr", "incon")),
#          response = factor(response, levels = c("correct", "incorrect"))) %>% 
#   select(task, response, cycle, activation) # just re-order slightly
# head(timecourse_task)
```

plot the data

```{r}
# p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
#   geom_line() +
#   ggtitle('Mean response activation by approach-avoid condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position="bottom") +
#   facet_wrap(~task)
# p1.4
# 
# ggsave ("sims/app_avoid/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
# p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
#   geom_line(aes(linetype=response)) +
#   # ggtitle('Mean response activation by condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
#         legend.title = element_text(size = 10, face = "bold"))  
# p1.5
# 
# ggsave ("sims/app_avoid/figures/timecourse_task2.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_search_easy
head(roc)
```

plot RT against accuracy

```{r}
p5.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=23.1", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p5.1

ggsave ("sims/search/figures/roc_rt_easy.jpeg")
```

## rt distrubition plots ##

density

```{r}
p6.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p6.1
```

boxplot

```{r}
# with acc=1
p6.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p6.2
```

violin plot

```{r}
# with acc=1
p6.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p6.3

ggsave ("sims/search/figures/rt_cycles_easy.jpeg")

# split by acc (if necessary)
p6.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p6.3b

```

combined plots

rt distributions

```{r}
p6.4 <- p6.1 / p6.2 / p6.3
p6.4

ggsave ("sims/search/figures/rt_dist_easy.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
# p3.5 <- p1.5 | p3.3
# p3.5 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.5
# 
# ggsave ("sims/search/figures/timecourse_rt_violin.jpeg")
```

with a boxplot

```{r}
# p3.6 <- p1.5 | p3.2
# p3.6 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.6
# 
# ggsave ("sims/app_avoid/figures/timecourse_rt_box.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='10' & acc == 1)$cycle, 
       subset(rts, task == '3' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/search/data/roc_easy.csv")
write_csv(rts, "sims/search/data/rts_easy.csv")
write_csv(rts_summary, "sims/search/data/rts_summary_easy.csv")
write_csv(tidy_t_cycle, "sims/search/data/tidy_t_cycle_easy.csv")
# write_csv(timecourse, "sims/search/data/timecourse.csv")
# write_csv(timecourse_task, "sims/search/data/timecourse_task.csv")
```


## section 3 ##

## take a look at simulated search data from the hard model ##

## read in the data files ##

read in relevant data files depending on how much wrangling needs doing. 

```{r}
out_search_hard <- read_csv("sims/search/data/out_search_hard.csv") 
head(out_search_hard)
rts_search_hard <- read_csv("sims/search/data/rts_search_hard.csv")
head(rts_search_hard)
roc_search_hard <- read_csv("sims/search/data/roc_search_hard.csv")
head(roc_search_hard)
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_search_hard %>%
  mutate(task = factor(task, levels = c("3", "10")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

This would need editing to be appropriate, given that it uses a different design
to the prior sims.

```{r}
# timecourse_task <- out_search_basic %>% 
#   select(task, cycle, correct_resp, incorrect_resp) %>% 
#   group_by(task, cycle) %>%
#   summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
#   pivot_longer(cols = c("correct", "incorrect"),
#                names_to = "response", values_to = "activation") %>% 
#   mutate(task = factor(task, levels = c("congr", "incon")),
#          response = factor(response, levels = c("correct", "incorrect"))) %>% 
#   select(task, response, cycle, activation) # just re-order slightly
# head(timecourse_task)
```

plot the data

```{r}
# p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
#   geom_line() +
#   ggtitle('Mean response activation by approach-avoid condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position="bottom") +
#   facet_wrap(~task)
# p1.4
# 
# ggsave ("sims/app_avoid/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
# p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
#   geom_line(aes(linetype=response)) +
#   # ggtitle('Mean response activation by condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
#         legend.title = element_text(size = 10, face = "bold"))  
# p1.5
# 
# ggsave ("sims/app_avoid/figures/timecourse_task2.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_search_hard
head(roc)
```

plot RT against accuracy

```{r}
p8.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=48.6", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p8.1

ggsave ("sims/search/figures/roc_rt_hard.jpeg")
```

## rt distrubition plots ##

density

```{r}
p9.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p9.1
```

boxplot

```{r}
# with acc=1
p9.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p9.2
```

violin plot

```{r}
# with acc=1
p9.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p9.3

ggsave ("sims/search/figures/rt_cycles_hard.jpeg")

# split by acc (if necessary)
p9.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p9.3b

```

combined plots

rt distributions

```{r}
p9.4 <- p9.1 / p9.2 / p9.3
p9.4

ggsave ("sims/search/figures/rt_dist_hard.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
# p3.5 <- p1.5 | p3.3
# p3.5 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.5
# 
# ggsave ("sims/search/figures/timecourse_rt_violin.jpeg")
```

with a boxplot

```{r}
# p3.6 <- p1.5 | p3.2
# p3.6 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.6
# 
# ggsave ("sims/app_avoid/figures/timecourse_rt_box.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='10' & acc == 1)$cycle, 
       subset(rts, task == '3' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/search/data/roc_hard.csv")
write_csv(rts, "sims/search/data/rts_hard.csv")
write_csv(rts_summary, "sims/search/data/rts_summary_hard.csv")
write_csv(tidy_t_cycle, "sims/search/data/tidy_t_cycle_hard.csv")
# write_csv(timecourse, "sims/search/data/timecourse.csv")
# write_csv(timecourse_task, "sims/search/data/timecourse_task.csv")
```


## section 4 ##

## take a look at simulated search data from the hard model, but only 85% accuracy ##

## read in the data files ##

read in relevant data files. 

```{r}
# if RT at 85% acc needs calculating, load this
out_search_hard <- read_csv("sims/search/data/out_search_hard.csv") 
head(out_search_hard)

# if RT at 85% acc has already been calculated, load these two files
rts_search_hard_85 <- read_csv("sims/search/data/rts_search_hard_85.csv")
head(rts_search_hard_85)
roc_search_hard_85 <- read_csv("sims/search/data/roc_search_hard_85.csv")
head(roc_search_hard_85)
```

## re-calculate RTs with 85% accuracy, rather than the default 98% ##

Skip this chunk if RTs at 85% acc have already been calculated.

This only needs computing once, after which you can just load the saved file.

```{r}
# rename df so that it runs with the RT script
out <- out_search_hard

# no calculate RTs with accuracy_required = .85
plan(multicore)
source("sims/RTs.R")

# In the search task, unlike the other sims, there are many alternative
# responses -- any location in the touch action map is a valid response
# (although only the target location is correct). The RTs_generate function
# needs to know about all these possibilities
# This gets all the unitnames in the touch action map (at11..at55). The correct
# response is always at53
at_units = colnames(out)[grep("at..", colnames(out))]

rt_data = RTs_generate(out, accuracy_required = .85, 
                       alternatives = at_units, target = "at53", 
                       epsilon = .001)
```

save out rt and roc data

```{r}
write_csv(rt_data[[1]], "sims/search/data/rts_search_hard_85.csv")
write_csv(rt_data[[2]], "sims/search/data/roc_search_hard_85.csv")
```

## wrangle rt data ##

```{r}
# make factors
rts <- rts_search_hard_85 %>%
  mutate(task = factor(task, levels = c("3", "10")))
head(rts)
str(rts)

# summarise accuracy data
acc_summary <- rts %>%
  group_by(task) %>%
  summarise(mean_acc = mean(acc), sd_acc=sd(acc))
head(acc_summary)
  
# summarise cycle data
rts_summary <- rts %>%
  group_by(task, acc) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
head(rts_summary)

# grand mean rt - useful for speed-accuracy plot
rts_mean <- rts %>%
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n))
head(rts_mean)

# grand mean accuracy - useful for speed-accuracy plot
rts_acc <- rts %>%
  summarise(mean_acc = mean(acc), sd=sd(acc), n=n(), sem=sd/sqrt(n))
head(rts_acc)
```

## look at the activation timecourse across parameters and conditions ##

## select relevant variables to plot ##

This would need editing to be appropriate, given that it uses a different design
to the prior sims.

```{r}
# timecourse_task <- out_search_basic %>% 
#   select(task, cycle, correct_resp, incorrect_resp) %>% 
#   group_by(task, cycle) %>%
#   summarise(correct = mean(correct_resp), incorrect = mean(incorrect_resp)) %>%
#   pivot_longer(cols = c("correct", "incorrect"),
#                names_to = "response", values_to = "activation") %>% 
#   mutate(task = factor(task, levels = c("congr", "incon")),
#          response = factor(response, levels = c("correct", "incorrect"))) %>% 
#   select(task, response, cycle, activation) # just re-order slightly
# head(timecourse_task)
```

plot the data

```{r}
# p1.4 <- ggplot(timecourse_task, aes(x = cycle, y = activation, color = response)) + 
#   geom_line() +
#   ggtitle('Mean response activation by approach-avoid condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position="bottom") +
#   facet_wrap(~task)
# p1.4
# 
# ggsave ("sims/app_avoid/figures/timecourse_task.jpeg")
```

and now re-plotted with overlap rather than facet_wrap

```{r}
# legend within the figure
# p1.5 <- ggplot(timecourse_task, aes(x = cycle, y = activation, colour = task)) + 
#   geom_line(aes(linetype=response)) +
#   # ggtitle('Mean response activation by condition') +
#   scale_color_brewer(palette = "Dark2") +
#   theme_bw() +
#   theme(text=element_text(size=18), title=element_text(size=18),
#         legend.position=c(0.8,0.5), legend.text = element_text(size=10), 
#         legend.title = element_text(size = 10, face = "bold"))  
# p1.5
# 
# ggsave ("sims/app_avoid/figures/timecourse_task2.jpeg")
```

## speed-accuracy curve ##

The response operating characteristic (ROC) curve. Each point on the curve represents a response threshold criterion and the resulting mean RT and mean accuracy. 

```{r}
roc <- roc_search_hard_85
head(roc)
```

plot RT against accuracy

```{r}
p11.1 <- ggplot(roc, aes(x = rt, y = acc)) +
  geom_line() + 
  geom_point(aes(x=rts_mean$mean_rt, y=rts_acc$mean_acc), shape=1, size = 3) +
  geom_vline(aes(xintercept=rts_mean$mean_rt), colour="blue") +
  geom_text(x=75, y=0.25, label="mean RT=33.1", colour = "blue", fontface=2) +
  geom_hline(aes(yintercept=rts_acc$mean_acc), colour="red") +
  geom_text(x=75, y=0.95, label="mean accuracy=98", colour = "red", fontface=2) +
  labs(title = "speed vs. accuracy curve",
       x = "RT (cycles)", y = "Accuracy (%)") +
  theme_bw() +
  xlim(0,200)
p11.1

ggsave ("sims/search/figures/roc_rt_hard_85.jpeg")
```

## rt distrubition plots ##

density

```{r}
p12.1 <- ggplot(rts, aes(x = cycle, colour = task)) +
  geom_density() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2")
p12.1
```

boxplot

```{r}
# with acc=1
p12.2 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_boxplot() +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2")
p12.2
```

violin plot

```{r}
# with acc=1
p12.3 <- ggplot(subset(rts, acc==1), aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=subset(rts_summary, acc==1), aes(y=mean_rt), size =3) +
  geom_errorbar(data=subset(rts_summary, acc==1), aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=subset(rts_summary, acc==1), aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") 
p12.3

ggsave ("sims/search/figures/rt_cycles_hard_85.jpeg")

# split by acc (if necessary)
p12.3b <- ggplot(rts, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position = "bottom") +
  facet_wrap(~acc) # # no need to facet_wrap when acc==1 on every sim
p12.3b

```

combined plots

rt distributions

```{r}
p12.4 <- p12.1 / p12.2 / p12.3
p12.4

ggsave ("sims/search/figures/rt_dist_hard_85.jpeg")
```

activation timecourse and rt

with a violin plot

```{r}
# p3.5 <- p1.5 | p3.3
# p3.5 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.5
# 
# ggsave ("sims/search/figures/timecourse_rt_violin.jpeg")
```

with a boxplot

```{r}
# p3.6 <- p1.5 | p3.2
# p3.6 + plot_annotation(tag_levels = 'A') &
#   theme(plot.tag = element_text(size = 16))
# #p3.6
# 
# ggsave ("sims/app_avoid/figures/timecourse_rt_box.jpeg")
```

## run a t-test on cycles ##

I'm not sure we need this tbh?? The plots look good enough to me. But it is here if that's what you want.

```{r}
t_test_cycle <- t.test(subset(rts, task=='10' & acc == 1)$cycle, 
       subset(rts, task == '3' & acc == 1)$cycle, paired = FALSE) 
t_test_cycle

# tidy the output with broom
tidy_t_cycle <- tidy(t_test_cycle)
tidy_t_cycle
```

## write out the files of interest ##

```{r}
write_csv(roc, "sims/search/data/roc_hard_85.csv")
write_csv(rts, "sims/search/data/rts_hard_85.csv")
write_csv(rts_summary, "sims/search/data/rts_summary_hard_85.csv")
write_csv(tidy_t_cycle, "sims/search/data/tidy_t_cycle_hard_85.csv")
# write_csv(timecourse, "sims/search/data/timecourse.csv")
# write_csv(timecourse_task, "sims/search/data/timecourse_task.csv")
```


## section 5 ##

## plot search data from different sims together ##

this is just for ease of comparison

# activation timecourse data #

not looked at or calculated yet.

# rt (cycles) #

load the data and add a noise variable

```{r}
rts_base <- read_csv("sims/search/data/rts.csv") %>% 
  mutate(difficulty = "baseline")
head(rts_base)

rts_easy <- read_csv("sims/search/data/rts_easy.csv") %>% 
  mutate(difficulty = "easy")
head(rts_easy)

rts_hard <- read_csv("sims/search/data/rts_hard.csv") %>% 
  mutate(difficulty = "hard_high_criterion")
head(rts_hard)

rts_hard_85 <- read_csv("sims/search/data/rts_hard_85.csv") %>% 
  mutate(difficulty = "hard_low_criterion")
head(rts_hard_85)
```

join them together and create a factor

```{r}
rts_all <- rbind(rts_base, rts_easy, rts_hard, rts_hard_85) %>%
  select(simno, task, difficulty, acc, cycle) %>% 
  mutate(task = factor(task, levels = c("3", "10")),
         difficulty = factor(difficulty, levels = c("baseline", "easy", "hard_high_criterion", "hard_low_criterion"))) %>% 
  filter(acc==1)
head(rts_all)
# summary(rts_all)
```

create summary data

```{r}
rts_all_summary <- rts_all %>%
  group_by(task, difficulty) %>% 
  summarise(mean_rt=mean(cycle), sd=sd(cycle), n=n(), sem=sd/sqrt(n)) 
rts_all_summary
```

plot

```{r}
p13.2 <- ggplot(rts_all, aes(x = task, y = cycle, fill = task)) +
  geom_violin() +
  geom_jitter(position=position_jitterdodge(dodge.width =1), alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_all_summary, aes(y=mean_rt), size =3) +
  geom_errorbar(data=rts_all_summary, aes(y = mean_rt, ymin=mean_rt-sem, ymax=mean_rt+sem), width=.2) +
  geom_line(data=rts_all_summary, aes(y=mean_rt, group=1)) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(0, 150)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("RT (cycles)") +
  facet_wrap(~difficulty, nrow=1)
p13.2

ggsave ("sims/search/figures/rt_cycles_all.jpeg")
```

now wrangle and plot the difference score or congruency effect

first wrangle the diff score or ce

```{r}
rts_diff <- rts_all %>% 
  pivot_wider(names_from = "task",
              values_from = "cycle") %>%
  mutate(ce = `10` - `3`) # use backticks when column names are numbers
rts_diff
# summary(rts_diff)
```

create a summary

```{r}
rts_diff_summary <- rts_diff %>%
  group_by(difficulty) %>% 
  summarise(mean_ce=mean(ce, na.rm=TRUE), sd=sd(ce, na.rm=TRUE), n=n(), sem=sd/sqrt(n))
rts_diff_summary  
```

then plot 

(with difficulty on the x-axis)

```{r}
p13.3 <- ggplot(rts_diff, aes(x = difficulty, y = ce)) +
  geom_violin() +
  geom_jitter(width=0.1, alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_diff_summary, aes(y=mean_ce), size =3) +
  geom_errorbar(data=rts_diff_summary, aes(y = mean_ce, ymin=mean_ce-sem, ymax=mean_ce+sem), width=.2) +
  theme_bw() +
  # scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(-10, 80)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold")) +
  ylab("Congruency Effect (cycles)") 
  # facet_wrap(~difficulty)
p13.3

ggsave ("sims/search/figures/ce_cycles_all.jpeg")
```

with difficulty as a facet_wrap (to help with a combined plot)

```{r}
p13.3b <- ggplot(rts_diff, aes(x = "", y = ce)) +
  geom_violin() +
  geom_jitter(width=0.1, alpha = 0.8, colour = "darkgrey") +
  geom_point(data=rts_diff_summary, aes(y=mean_ce), size =3) +
  geom_errorbar(data=rts_diff_summary, aes(y = mean_ce, ymin=mean_ce-sem, ymax=mean_ce+sem), width=.2) +
  theme_bw() +
  scale_fill_brewer(palette = "Dark2") +
  # scale_y_continuous(limits = c(-10, 80)) +
  theme(text=element_text(size=18), title=element_text(size=18),
        legend.position="none", legend.text = element_text(size=10), 
        legend.title = element_text(size = 10, face = "bold"),
        axis.title.x=element_blank(), axis.ticks.x=element_blank()) +
  ylab("Congruency Effect (cycles)") +
  facet_wrap(~difficulty, nrow = 1)
p13.3b

# ggsave ("sims/search/figures/ce_cycles_all.jpeg")
```

now combine RT and CE plots together

```{r}
p13.4 <- p13.2 / p13.3b
p13.4

ggsave ("sims/search/figures/rt_ce_cycles_all.jpeg")
```

## print session info #

```{r}
sessionInfo()
```

