---
title: "search_sim"
author: "Rob & Rich"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file runs src simulations for the visual search task.

There are three different types of simulation that can be run.

1. Base (serves as default or baseline).

2. Easy. Increase the within-map inhibition.

3. Hard. Reduce the within-map inhibition.

## clear everything to start with a fresh environment ##

```{r}
rm(list = ls())
```

## Load the libraries we will be using ##

see packages.Rmd in the /5x5/ folder

## simulations 1, 2 & 3 ##

## run the simulation ##

choose one of the below chunks

A uniquely named .RData file is automatically saved in /data/rdata/

sim 1 - basic task with standard settings

```{r}
plan(multicore)
source('sims/search/search_run.R')
```

sim 2 - Easy. Increase the within-map inhibition.

```{r}
plan(multicore)
source('sims/search/search_run_easy.R')
```

sim 3 - Hard Decrease the within-map inhibition.

```{r}
plan(multicore)
source('sims/search/search_run_hard.R')
```

## save out .csv files ##

choose one of the below chunks

```{r}
#sim1
write_csv(out, "sims/search/data/out_search.csv")
```

```{r}
#sim2
write_csv(out, "sims/search/data/out_search_easy.csv")
```

```{r}
#sim3
write_csv(out, "sims/search/data/out_search_hard.csv")
```

## calculate RT data ##

```{r}
plan(multicore)
source('sims/RTs.R')
# In the search task, unlike the other sims, there are many alternative
# responses -- any location in the touch action map is a valid response
# (although only the target location is correct). The RTs_generate function
# needs to know about all these possibilities
# This gets all the unitnames in the touch action map (at11..at55). The correct
# response is always at53
at_units = colnames(out)[grep("at..", colnames(out))]

#' With all the response alternatives, it's useful to vary the criterion
#' relatively slowly, by using a small epsilon incremental value
rt_data = RTs_generate(out, accuracy_required = .98, 
                       alternatives = at_units, target = "at53", 
                       epsilon = .001)

# some basic RT comparisons follow
rt_overview(rt_data)
```

## save the RT data ##

choose one of the below chunks

```{r}
#sim1
write_csv(rt_data[[1]], "sims/search/data/rts_search.csv")
write_csv(rt_data[[2]], "sims/search/data/roc_search.csv")
```

```{r}
#sim2
write_csv(rt_data[[1]], "sims/search/data/rts_search_easy.csv")
write_csv(rt_data[[2]], "sims/search/data/roc_search_easy.csv")
```

```{r}
#sim3
write_csv(rt_data[[1]], "sims/search/data/rts_search_hard.csv")
write_csv(rt_data[[2]], "sims/search/data/roc_search_hard.csv")
```

## print session info ##

```{r}
sessionInfo()
```